---
title: "Integrated Collision Research"
author: "Kaylei Holthe, Yuxin Chen, Bobby Deng, Steven Bao"
date: "May 24, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(rworldmap)
library(RColorBrewer)
library(knitr)
library(lubridate)
library(stringr)
library(leaflet)
library(lintr)
library(ggmap)
library(stats)
library(reshape)
source("scripts/chart1.R")
source("scripts/chart2.R")
source("scripts/chart3.R")
source("scripts/summary.R")
source("scripts/table.R")

df_2018 <- read.csv("data/df_2018.csv", stringsAsFactors = F)
```
## Introduction
This is an analysis of Seattle collision data, specifically from 2018. The data
set includes various details of collisions like places of incidents, people 
involved and severity of collisions. We are interested in what factors effect 
collisions the greatest such as time, weather conditions and pedestrian
involvement.

## Summary of Project
In 2018 there were `r test$number_crashes` of crashes. There were a total
of `r test$total_fatalities` fatalities. The type of junction with the most 
incidents in
2018 was `r test$most_junction`. The total amount of pedestrians involved in car
collisions was `r test$ped_injuries`. `r test$most_day_of_week` was the weekday 
that the most collisions occurred on.

## Summary Table
```{r make_table(), echo=FALSE}
make_table(df_2018)
```

This is a table showing the summary information about all types of collisions in 
Seattle area in 2018 sorted by the number of total cases.
It contains information of the number of people in 
different levels of injuries or even fatality. We include this table in order 
to provide clear information on the frequency of each type of collision and its 
severity from the casualties.

## Map of Collisions
```{r map_fun(), echo = FALSE, message = FALSE}
map_fun(df_2018)
```

This is a map showing all traffic accidents in the chosen year. And we can see 
that accidents most happen in downtown area. From the map, we can see the 
distribution and the propensity of traffic accidents. We include this map in 
order to give a basic sense about how accidents are distributed in Seattle 
around 2018.

## Pedestrian and Cyclist Involvement
```{r cyclists_map(), echo = FALSE}
ped_cycle_plot(df_2018)
```

This map visualizes the number of pedestrians and cyclists involved in Seattle 
car collisions at different times of day.

## Relationships Between Weather Conditions and Fatalities
```{r pie_chart_fun(), echo = FALSE}
pie_chart_fun(df_2018)
```

This pie chart shows the fatalities in different weather conditions in Seattle 
car collisions. From the chart we can see that in "clear or partly cloudy" and 
"Raining" conditions had the largest amount of fatalities.